---
title: "Assignment: 2021 VAST Mini Challenge 2"
description: |
  The Kronos Incident
author:
  - name: Connie Xia
    url: https://example.com/conniexia
date: 07-25-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

## Introduction

This Visual Analytics Assignment is based on the VAST Challenge 2021 Mini Challenge 2. The overview of the Challenge is about a Tethys-based GAStech that has been operating a natural gas production site in the island country og Kronos. Despite bringing in remarkable profits and developing strong relationships with the Kronos government, GAStech has not been as successful in demonstrating environmental stewardship.

In January 2014, while the leaders of GAStech were celebrating their successful initial public offering (IPO), several of the company's employees go missing. It is suspected that an organisation called the Protectors of Kronos (POK) was involved in the employees' disappearance, but things may not be what they seem. 

## The Mini Challenge
Mini Challenge 2 is about analysing the movement and tracking data of the GAStech employees, as well as their card card transactions and loyalty card usage data. From which, any anomalies and suspicious behaviours of the GAStech employees will be identified and analysed. 


## Literature Reviews
Here. 


## Data Sources
The data sources used in the mini challenge are:

Data sources | Description 
---------------- | ---------------- 
car-assignments.csv | List of vehicle assignments by employee
Geospatial folder | ESRI shapefiles of Abila and Kronos
gps.csv | Vehicle tracking data
loyalty_data.csv | Loyalty card transaction data
cc_data.csv | Credit and debit card transaction data
MC2-Tourist.jpg | Tourist map of Abila with locations of interest identified

## R Packages Used
Below are the list of R packages installed and used in this assignment. 

```{r}
packages = c('raster', 'sf', 'tmap', 'lubridate', 
             'tidyverse', 'igraph', 'tidygraph', 
             'ggraph', 'visNetwork', 'clock',
             'DT', 'zoo', 'parcoords')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}
```


## Location Analysis

### Data Preparation

The credit card and loyalty card csv files are first loaded into R. 

```{r}
cc_data <- read_csv("./data/cc_data.csv")
loyalty_data <- read_csv("./data/loyalty_data.csv")
```

Taking a look at the two datasets, we can observe that the *timestamp*, *location* and *loyaltynum* are in character field while *price* and *last4ccnum* are in numerical field. It is to be noted that the *timestamp* field should be in date-time format.

```{r}
glimpse(cc_data)
glimpse(loyalty_data)
```

Therefore, we need to convert the *timestamp* field in both datasets from character type to date-time type. 

```{r}
cc_data$timestamp <- date_time_parse(cc_data$timestamp,
                                     zone = "",
                                     format = "%m/%d/%Y %H:%M")

loyalty_data$timestamp <- date_time_parse(loyalty_data$timestamp,
                                          zone = "",
                                          format = "%m/%d/%Y")

```

Now, all the fields are in their correct data type.

```{r}
glimpse(cc_data)
glimpse(loyalty_data)
```

In order to have a better understanding and visualisation on how the credit card and loyalty card usage are related, we would need to join both datasets together. 

First, it is noted that the *timestamp* column in the *cc_data* dataset has both dates and time, while the *timestamp* column in the *loyalty_data* dataset only has the date field. So, we need to extract out the *date* from the *timestamp* column of the *cc_data*.

```{r}
cc_data$date <- format(cc_data$timestamp, "%m/%d/%Y")
cc_data$date <- date_time_parse(cc_data$date, 
                                zone = "", 
                                format = "%m/%d/%Y")

head(cc_data)
head(loyalty_data)
```

Now, we can join both datasets together by the *date*, *price* and *location*. A new column, *hour*, is added to take note of the time period the employee visited the location.

```{r}
cc_loyalty_data <- left_join(cc_data, loyalty_data,
                             by = c("date" = "timestamp",
                                    "location" = "location",
                                    "price" = "price"))

cc_loyalty_data$hour = hour(cc_loyalty_data$timestamp)
  
glimpse(cc_loyalty_data)
```

### Data Visualisation
Exploratory data analysis is conducted to determine the most popular locations frequented by the employees of GAStech. 

Looking at the combined dataset, we are able to observe that the top five most popular locations are:

1. Katerina's Cafe
2. Hippokampos
3. Guy's Gyros
4. Brew've Been Served
5. Hallowed Grounds

```{r}
freq_by_location <- cc_loyalty_data %>%
  select(location, price) %>%
  group_by(location) %>%
  summarise(total_price = sum(price), freq = n()) %>%
  arrange(desc(freq)) %>%
  ungroup()

ggplot(data=freq_by_location,
       aes(x = reorder(location, -freq), y = freq)) +
  geom_col() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) + 
  ggtitle("Frequency of Visit") +
  labs(y = "Frequency", x = "Location")
```

Delving deeper into the top 5 most frequented places over the span of two weeks, we can plot a calendar heatmap to show the frequencies of purchases made at the top 5 most popular locations. 


```{r}
freq_by_date <- cc_loyalty_data %>%
  select(date, hour, location, price) %>%
  group_by(date, hour, location) %>%
  summarise(total_price = sum(price), freq = n()) %>%
  arrange(desc(freq)) %>%
  ungroup()

freq_by_date$weekday = as.POSIXlt(freq_by_date$date, format = "%d/%m/%Y")$wday

freq_by_date$weekdayf <- factor(freq_by_date$weekday, 
                                levels = rev(0:6),
                                labels = rev(c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")),
                                ordered = TRUE)

top5_plot <- freq_by_date %>%
  na.omit() %>%
  filter(location %in% c("Katerina's Cafe", "Hippokampos", "Guy's Gyros", "Brew've Been Served", "Hallowed Grounds"))

top5_heatmap <- ggplot(top5_plot, aes(hour, weekdayf, fill = top5_plot$freq)) +
  geom_tile(colour = "white") +
  facet_grid(~location) +
  theme(strip.text = element_text(size = 7)) +
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  xlab("Hour") + 
  xlim(c(0,23)) +
  ylab("Day") + 
  ggtitle("Calendar Heatmap: Transaction Volume at Top 5 Locations") + 
  labs(fill = "Frequency")

top5_heatmap

```

The following observations and insights can be derived from the calendar heatmap:

1. All 5 locations are possibly dining places located in Abila inferred from the time period the employees visited those locations.
2. Brew've Been Served is a popular location during the weekdays around breakfast hours (0700-0800). Similarly, Hallowed Grounds is probably another popular breakfast place during the weekdays.
3. Guy's Gyros, Hippokampos and Katerina's Cafe are popular lunch (1300-1400) and dinner (1900-2100) spots throughout the entire week.

Moving on, two other calendar heatmaps are plotted to view the transaction volume comparison between weekdays and weekends. 

```{r}

weekday_plot <- freq_by_date %>%
  na.omit() %>%
  filter(weekday %in% c(1:5))

weekday_heatmap <- ggplot(weekday_plot, aes(hour, location, fill = weekday_plot$freq)) +
  geom_tile(colour = "white") +
  theme(strip.text = element_text(size = 7)) +
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  xlab("Hour") + 
  xlim(c(0,23)) +
  ylab("Location") + 
  ggtitle("Calendar Heatmap: Transaction Volume during Weekdays") + 
  labs(fill = "Frequency")

weekday_heatmap

```

```{r}

weekend_plot <- freq_by_date %>%
  na.omit() %>%
  filter(weekday %in% c(0,6))

weekend_heatmap <- ggplot(weekend_plot, aes(hour, location, fill = weekend_plot$freq)) +
  geom_tile(colour = "white") +
  theme(strip.text = element_text(size = 7)) +
  scale_fill_distiller(palette = "Reds", direction = 1) + 
  xlab("Hour") + 
  xlim(c(0,23)) +  
  ylab("Location") + 
  ggtitle("Calendar Heatmap: Transaction Volume during Weekends") + 
  labs(fill = "Frequency")

weekend_heatmap

```

A boxplot show the spread of the transaction amount made by GAStech employees at different locations.

```{r}
median_price <- cc_loyalty_data %>%
  group_by(location) %>%
  summarise(median_price = median(price))

spending_by_location <- cc_loyalty_data %>%
  left_join(median_price, 
            by = c("location"))

ggplot(data = spending_by_location,
       aes(x = reorder(location, -median_price), y = price)) +
  geom_boxplot(outlier.colour = "Red", outlier.fill = "Red") +
  geom_point(alpha = 0) +
  scale_y_log10() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1,
                                   vjust = 0.5)) + 
  ggtitle("Transaction Amount by Location") +
  labs(y = "Spending amount", x = "Location")
``` 

Based on the above plots, we are able to spot a few anormalies that are note-worthy. 

1. Kronos Mart

From both the weekday and weekend calendar maps plotted above, there are transactions occurring at that location at the wee hours, when most people would be asleep. Further analysis revealed that there are a total of 5 transactions occurring on 3 different days (12 Jan, 13 Jan and 19 Jan) around 0300-0400 time period. The 5 transactions are all carried out on different credit cards, with no loyalty card used. It is also suspicious that the last two transactions occurred within the span of three minutes, suggesting a likely possibility that the last two card owners might have seen each other in the mart.

```{r}
knitr::kable(cc_loyalty_data %>%
               filter(location %in% "Kronos Mart" & hour %in% 3) %>%
               dplyr::select(location, timestamp, date, hour, price, last4ccnum, loyaltynum) %>%
               arrange(hour), "simple",
             caption = "Transactions made in Kronos Mart")
```


2. Frydos Autosupply n' More

Based on the boxplot plotted above, we are able to identify an outlier transaction at Frydos Autosupply n' More. There is an exceptionally high transaction of 10,000 dollars at the store where the median price is 149.30 dollars. Similarly, this transaction was not tagged to any loyalty card.  

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Frydos Autosupply n' More") %>%
               filter(price %in% max(price)) %>%
               dplyr::select(location, timestamp, date, hour, price, median_price, last4ccnum, loyaltynum),
             caption = "Transactions made in Frydos Autosupply n' More")
```

3. Daily Dealz

Despite being a low transaction amount, this purchase is rather suspicious as that is not tied to any loyalty card. The maximum, median and minimum transaction amounts also seem to be the same value, suggesting that it could be a singular purchase. This also means that not many people make purchases from Daily Dealz over the span of two weeks. Further analysis confirmed the suspicion. Furthermore, the credit card used to make the purchase is same as the credit card used to make the hefty purchase at Frydos Autosupply n' More. The timing where the transaction occurred is also rather suspicious as it is an early morning purchase.

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Daily Dealz") %>%
               dplyr::select(location, timestamp, date, hour, price, last4ccnum, loyaltynum) %>%
               arrange(hour), "simple",
             caption = "Transactions made in Daily Dealz")
```

4. Albert's Fine Clothing

Based on the boxplot plotted above, we are able to identify an outlier transaction at Albert's Fine Clothing. There is large transaction of 1,239.41 dollars compared to the median spending amount of 211.47 dollars. 

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Albert's Fine Clothing") %>%
               filter(price %in% max(price)) %>%
               dplyr::select(location, timestamp, date, hour, price, median_price, last4ccnum, loyaltynum), 
             caption = "Transactions made in Albert's Fine Clothing")
```

5. Chostus Hotel

Based on the boxplot plotted above, we are able to identify an outlier transaction at Chostus Hotel. There is a higher than average transaction of 600 dollars compared to the median spending amount of 114.22 dollars. 

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Chostus Hotel") %>%
               filter(price %in% max(price)) %>%
               dplyr::select(location, timestamp, date, hour, price, median_price, last4ccnum, loyaltynum), 
             caption = "Transactions made in Chostus Hotel")
```

6. Credit Card Number 9551

This credit card is highly suspicious due to the fact that it is used in three of the alleged suspicious transactions pointed out above at Kronos Mart, Frydos Autosupply n' More and Daily Dealz. Upon inspection of the card transaction detail, we can see that the card owner does have a loyalty card, but it seems like they tend to selectively use their loyalty card for discounts. 

Another dubious point to note is that for the first week, they use their credit card daily but during the next week, there are gaps in the transactions. Especially after 13 Jan (Mon), the credit card user stopped using their card for a few days before making transactions on 16 Jan (Thu).

```{r}
cc_loyalty_data$weekday = as.POSIXlt(cc_loyalty_data$date, format = "%d/%m/%Y")$wday

cc_loyalty_data$weekdayf <- factor(cc_loyalty_data$weekday, 
                                levels = rev(0:6),
                                labels = rev(c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat")),
                                ordered = TRUE)

knitr::kable(cc_loyalty_data %>%
               filter(last4ccnum %in% 9551) %>%
               dplyr::select(timestamp, weekdayf, location, price, last4ccnum, loyaltynum), 
             caption = "Transactions made with CC 9551")
```