---
title: "Assignment: Part 2"
description: |
    The Kronos Incident
author:
  - name: Connie Xia
    url: https://example.com/conniexia
date: 07-28-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3,
                      echo = TRUE, 
                      eval = TRUE,
                      message = FALSE,
                      warning = FALSE)

packages = c('raster', 'sf', 'tmap', 'lubridate', 
             'tidyverse', 'igraph', 'tidygraph', 
             'ggraph', 'visNetwork', 'clock',
             'DT', 'zoo', 'parcoords', 'mapview')
for (p in packages){
  if(!require(p, character.only = T)){
    install.packages(p)
  }
  library(p, character.only = T)
}

cc_data <- read_csv("./data/cc_data.csv")
loyalty_data <- read_csv("./data/loyalty_data.csv")

cc_data$timestamp <- date_time_parse(cc_data$timestamp,
                                     zone = "",
                                     format = "%m/%d/%Y %H:%M")

loyalty_data$timestamp <- date_time_parse(loyalty_data$timestamp,
                                          zone = "",
                                          format = "%m/%d/%Y")

cc_data$date <- format(cc_data$timestamp, "%m/%d/%Y")
cc_data$date <- date_time_parse(cc_data$date, 
                                zone = "", 
                                format = "%m/%d/%Y")

cc_loyalty_data <- left_join(cc_data, loyalty_data,
                             by = c("date" = "timestamp",
                                    "location" = "location",
                                    "price" = "price"))

cc_loyalty_data$hour = hour(cc_loyalty_data$timestamp)

median_price <- cc_loyalty_data %>%
  group_by(location) %>%
  summarise(median_price = median(price))

spending_by_location <- cc_loyalty_data %>%
  left_join(median_price, 
            by = c("location"))

bgmap <- raster("./data/MC2-tourist.tif")

Abila_st <- st_read(dsn = "./data/Geospatial",
                    layer = 'Abila')

gps <- read_csv("./data/gps.csv")
gps$Timestamp <- date_time_parse(gps$Timestamp,
                                 zone = "",
                                 format = "%m/%d/%Y %H:%M")

gps$day <- as.factor(get_day(gps$Timestamp))

gps$id <- as.factor(gps$id)

gps_sf <- st_as_sf(gps,
                   coords = c("long", "lat"),
                   crs = 4326)

gps_path <- gps_sf %>%
  group_by(id, day) %>%
  summarise(m = mean(Timestamp),
            do_union = FALSE) %>%
  st_cast("LINESTRING")

POI <- gps_sf %>%
  group_by(id) %>%
  mutate(stoptime = Timestamp - lag(Timestamp)) %>%
  mutate(parked = ifelse(stoptime > 60*3, TRUE, FALSE)) %>%
  ungroup() %>%
  filter(parked == TRUE) %>%
  group_by(id, day) %>%
  add_count(id, day, name = "count") %>%
  ungroup()

POI_sf <- POI %>%
  filter(parked == TRUE)

```


Observations:

* Car ID 24 left U-Pump at 13:22, corresponding to the transaction at U-Pump occurring at 13:18. 
* The user of Car ID 24 was near the area of Brew've Been Served at 19:29 whereas another transaction was made at Ouzeri Elian at 19:30.

Conclusion: 
The user of Car ID 24 and the holder of CC 9551 might not be the same person as the card and car records do not match perfectly, making the transactions on CC 9551 very suspicious. We can infer that perhaps the CC 9951 was used by more than one person. 


2. The next anormaly is the transactions made during the wee hours at Kronos Mart.

These five different transactions are all made by different credit cards, suggesting that it might be not a habit of an individual who prefers to grocery shop at night.

```{r}
knitr::kable(cc_loyalty_data %>%
               filter(location == "Kronos Mart" & hour == "3") %>%
               dplyr::select(timestamp, location, price, last4ccnum, loyaltynum) %>%
               arrange(timestamp), "simple",
             caption = "Transactions made at Kronos Mart during the wee hours")
```

Looking at the stationary points of the cars on 12, 13 and 19 Jan, we aren't able to point out which car is linked to the credit cards used at the mart. The only stationary points appearing near Kronos Mart are:

* 12 Jan, 13:58 
* 13 Jan, 13:38
* 19 Jan, 14:23

These timings all do not coincide with the timings in the wee hours.

```{r}
POI_midnight <- POI_sf %>%
  filter(day == c(12, 13, 19))
tmap_mode("view")

tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(POI_midnight) +
  tm_dots(col = "blue")
```

Conclusion:
The credit card holders of 8156, 5407, 3484, 9551 and 8332 either stay a walking distance from the Kronos Mart or they used their own personal cars instead of the company-provide cars to make the travel. 


3. Another anormaly has to do with the large transaction occurring at Albert's Fine Clothing and Chostus Hotel. 

Looking at the Albert's Fine Clothing suspicious transaction, we can see that the transaction occurred on 17 Jan at 19:44, using CC 1321 and L4149.

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Albert's Fine Clothing") %>%
               filter(price %in% max(price)) %>%
               dplyr::select(location, timestamp, date, hour, price, median_price, last4ccnum, loyaltynum), 
             caption = "Transactions made in Albert's Fine Clothing")
```

Hence, when we plot out the stationary locations on the map (on 17 Jan, between 1900-2000), we are able to observe that Car ID 11 left the clothing store at 19:46, which matched up to the suspicious transaction time. Hence, it can be implied that the owner of Car ID 11 might hold CC 1321 and L4149.

```{r}
POI_sf$hour = hour(POI_sf$Timestamp)

POI_clothing <- POI_sf %>%
  filter(day == 17 & hour == 19)
tmap_mode("view")

tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(POI_clothing) +
  tm_dots(col = "blue")
```


Similarly, we can see that the dubious transaction at Chostus Hotel occurred on 18 Jan at 12:03. The credit card in question is 5010, tied to a loyalty card L2459.

```{r}
knitr::kable(spending_by_location %>%
               filter(location %in% "Chostus Hotel") %>%
               filter(price %in% max(price)) %>%
               dplyr::select(location, timestamp, date, hour, price, median_price, last4ccnum, loyaltynum), 
             caption = "Transactions made in Chostus Hotel")
```

Plotting the stationary points on the map, we can see that Car ID 31 left the hotel at 12:35, which matches up with the transaction data. Hence, it is implied that the owner of Car ID 31 might be the holder of CC 5010. 

```{r}
POI_hotel <- POI_sf %>%
  filter(day == 18 & hour == 12)
tmap_mode("view")

tm_shape(bgmap) +
  tm_rgb(bgmap, r = 1,g = 2,b = 3,
       alpha = NA,
       saturation = 1,
       interpolate = TRUE,
       max.value = 255) +
  tm_shape(POI_hotel) +
  tm_dots(col = "blue")

```


## Respective Owners of Credit and Loyalty Cards

Moving on, we will be trying to see if we can derive the respective owners of the credit and loyalty cards.

The unique counts of the credit cards and loyalty cards are 55 and 54 respectively. This suggests that there might be duplicate usages of either credit or loyalty cards. 

```{r}
unique_cc <- unique(cc_data$last4ccnum)
length(unique_cc)

unique_loyalty <- unique(loyalty_data$loyaltynum)
length(unique_loyalty)
```

First, we will be joining the two datasets by the *day*, *location* and *price*.

```{r}
cc_data$day <- as.factor(get_day(cc_data$timestamp))

loyalty_data$day <- as.factor(get_day(loyalty_data$timestamp))

ccloy <- merge(cc_data, loyalty_data,
               by = c("day", "location", "price")) %>%
  select("timestamp.y", "timestamp.x", "day", "location", "price", "last4ccnum", "loyaltynum")

glimpse(ccloy)
```

Then, we pulled out all of the unique tags to each credit and loyalty card. There is a total of 62 entries, which means that there might be duplicate usage of either credit or loyalty cards.

```{r}
unique_tag <- ccloy %>%
  select("last4ccnum", "loyaltynum") %>%
  distinct(last4ccnum, loyaltynum, .keep_all = TRUE) %>%
  ungroup()

unique_tag$last4ccnum = as.factor(unique_tag$last4ccnum)

DT::datatable(unique_tag, 
              options = list(
                autoWidth = FALSE,
                columnDefs = list(list(width = '1px',
                                       className = 'dt-center',
                                       targets = c(0,1,2))))) %>%
  formatStyle(0,
              target = 'row',
              lineHeight='75%')
```

We also plotted an interactive parallel coordinates plot to see which credit cards and loyalty cards are linked together.

```{r}
parcoords(
 unique_tag[,1:2],
 rownames = FALSE,
 reorderable = T,
 brushMode = '1D-axes')
```

Taking at a look at the duplicates, we can see that there are a total of 7 credit cards that are linked to 2 different loyalty cards each.

```{r}
cc_duplicates = unique_tag[duplicated(unique_tag$last4ccnum)|duplicated(unique_tag$last4ccnum, fromLast=TRUE),] %>%
  arrange(last4ccnum)

DT::datatable(cc_duplicates, 
              options = list(
                autoWidth = FALSE,
                columnDefs = list(list(width = '1px',
                                       className = 'dt-center',
                                       targets = c(0,1,2))))) %>%
  formatStyle(0,
              target = 'row',
              lineHeight='75%')

```

Similarly, for the loyalty cards, there are a total of 8 loyalty cards that are used for 2 different credit card holders.

```{r}
loyalty_dups = unique_tag[duplicated(unique_tag$loyaltynum)|duplicated(unique_tag$loyaltynum, fromLast=TRUE),] %>%
  arrange(loyaltynum)

loyalty_dups <- loyalty_dups[, c("loyaltynum", "last4ccnum")]

DT::datatable(loyalty_dups, 
              options = list(
                autoWidth = FALSE,
                columnDefs = list(list(width = '1px',
                                       className = 'dt-center',
                                       targets = c(0,1,2))))) %>%
  formatStyle(0,
              target = 'row',
              lineHeight='75%')

```

Yet there are uncertainties in the data. The credit card data is timestamped with both date and time while the loyalty card data is timestamped with only dates. This would mean that some matching of data might not be accurate, if there are more than one transactions of the same amount in the same day but at different timings, yet tagged to different credit and loyalty cards. Under this circumstance, it would make it difficult for us to determine which credit card is linked to which loyalty card.
    
## Informal/Unofficial relationships among GASTech Personnel

To look at the informal relationships among the GASTech employees, we first merged the gps data with the car assignment data.

```{r}
car <- read_csv("data/car-assignments.csv")

car$CarID = as.factor(car$CarID)

glimpse(car)
```

```{r}
merged_gps <- left_join(gps, car, 
                        by = c("id" = "CarID"))

merged_gps <- merged_gps[with(merged_gps, order(id,Timestamp)),]

merged_gps <- merged_gps %>% 
  mutate(diff = Timestamp - lag(Timestamp, default = first(Timestamp)))
merged_gps$diff_hr <- round(merged_gps$diff / 60 / 60, 1) 

geog <- merged_gps %>% 
  filter(diff > 600)

glimpse(geog)

```

We then assigned the geographical locations to the corresponding area represented by the longitudes and latitudes. 

```{r}
geog$poi <- 1 
geog <- geog %>% 
  mutate(poi = case_when(
    between(lat, 36.05092013, 36.05102938) & 
      between(long, 24.82586806, 24.82598723)  ~ "Abila Airport", 
    between(lat, 36.07434876, 36.07443715) & 
      between(long, 24.84592966, 24.84598782)  ~ "Abila Scrapyard", 
    between(lat, 36.06342076, 36.06349309) & 
      between(long, 24.85096457, 24.85103679)  ~ "Abila Zacharo", 
    between(lat, 36.07712237, 36.07715385) & 
      between(long, 24.87617634, 24.87621582)  ~ "Ahaggo Museum",
    between(lat, 36.07522801, 36.07530344) & 
      between(long, 24.85626503, 24.85634849)  ~ "Albert's Fine Clothing",
    between(lat, 36.08172086, 36.08182543) & 
      between(long, 24.85086882, 24.85096705)  ~ "Bean There Done That",
    between(lat, 36.05402149, 36.05413903) & 
      between(long, 24.90116515, 24.90128202)  ~ "Brew've Been Served", 
    between(lat, 36.07332048, 36.07336116) & 
      between(long, 24.86416419, 24.86420583)  ~ "Brewed Awakenings", 
    between(lat, 36.05851786, 36.05860144) & 
      between(long, 24.8808655, 24.88092654)  ~ "Carlyle Chemical Inc.", 
    between(lat, 36.07062423, 36.07073983) & 
      between(long, 24.89517609, 24.89526281)  ~ "Chostus Hotel",
    between(lat, 36.05462322, 36.05469486) & 
      between(long, 24.88977034, 24.88983886)  ~ "Coffee Cameleon", 
    between(lat, 36.08954231, 36.08962196) & 
      between(long, 24.86066508, 24.8607611)  ~ "Desafio Golf Course", 
    between(lat, 36.07212045, 36.07213193) & 
      between(long, 24.84132949, 24.84134818)  ~ "Frank's Fuel", 
    between(lat, 36.05492145, 36.05503511) & 
      between(long, 24.90176782, 24.90188061)  ~ "Frydos Autosupply n' More", 
    between(lat, 36.04802098, 36.04805422) & 
      between(long, 24.87956497, 24.87957691)  ~ "GasTech", 
    between(lat, 36.05970763, 36.05981097) & 
      between(long, 24.85797552, 24.8580772)  ~ "Gelatogalore", 
    between(lat, 36.06034564, 36.06043016) & 
      between(long, 24.85646426, 24.85657454)  ~ "General Grocer", 
    between(lat, 36.05572125, 36.05584094) & 
      between(long, 24.90246542, 24.90258487)  ~ "Guy's Gyros", 
    between(lat, 36.06362146, 36.06371539) & 
      between(long, 24.88586605, 24.88595859)  ~ "Hallowed Grounds", 
    between(lat, 36.07660977, 36.07669909) & 
      between(long, 24.85756408, 24.85764247)  ~ "Hippokampos", 
    between(lat, 36.06749651, 36.0675518) & 
      between(long, 24.87330651, 24.873366)  ~ "Jack's Magical Beans", 
    between(lat, 36.06582037, 36.06584879) & 
      between(long, 24.85236427, 24.85241027)  ~ "Kalami Kafenion", 
    between(lat, 36.05442247, 36.05453641) & 
      between(long, 24.89986596, 24.89998054)  ~ "Katerina’s Café",
    between(lat, 36.05292229, 36.05296701) & 
      between(long, 24.84936915, 24.84941679)  ~ "Kronos Capital", 
    between(lat, 36.06582196, 36.06587998) & 
      between(long, 24.8497762, 24.84983936)  ~ "Kronos Mart", 
    between(lat, 36.06523446, 36.06534083) & 
      between(long, 24.83307421, 24.83318494)  ~ "Kronos Pipe and Irrigation", 
    between(lat, 36.06402993, 36.06410072) & 
      between(long, 24.84137818, 24.84144338)  ~ "Maximum Iron and Steel", 
    between(lat, 36.05840347, 36.05849041) & 
      between(long, 24.88546548, 24.88553455)  ~ "Nationwide Refinery", 
    between(lat, 36.05859158, 36.05859887) & 
      between(long, 24.85790261, 24.85799357)  ~ "Octavio's Office Supplies", 
    between(lat, 36.05192066, 36.05197575) & 
      between(long, 24.87076418, 24.87082137)  ~ "Ouzeri Elian", 
    between(lat, 36.06324941, 36.06330782) & 
      between(long, 24.85226894, 24.8523291)  ~ "Roberts and Sons", 
    between(lat, 36.05282139, 36.05288367) & 
      between(long, 24.86856868, 24.8686314)  ~ "Shoppers' Delight", 
    between(lat, 36.05409586, 36.05420832) & 
      between(long, 24.90806584, 24.90817838)  ~ "Stewart and Sons Fabrication", 
    between(lat, 36.06774029, 36.06776587) & 
      between(long, 24.87148791, 24.87150031)  ~ "U-Pump",
    ))

glimpse(geog)

```

One location to identify for informal relationship will be the Chostus Hotel. 

```{r}
hotel <- geog %>% 
  filter(poi == "Chostus Hotel") %>%
  select( poi, Timestamp, id, LastName, FirstName, CurrentEmploymentTitle, CurrentEmploymentType)

knitr::kable(hotel %>%
               arrange(Timestamp),
             caption = "Records in Chostus Hotel")
```

We are able to suspect that Elsa Orilla and Brand Tempestad might have a relationship going on between them, as the both of them has frequented the hotel on four separate days. 

## Evidence of Suspicious Activities

Based on the analysis conducted above, we are able to point out several suspicious activities occurring. 

1. The $10,000 transaction at Frydos Autosupply n' More could be due to fraud as our analysis tells us that the credit card 9951 might have be stolen by another person to make that transaction. 

2. The consistent late night transactions at Kronos Mart needs to be investigated.

